\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-31 docs/parco13/paper.tex
Edit
Adding omp results.

@@

We would like to thank the Texas Advanced Computing Center (TACC) for access to
the Stampede supercomputer under allocation TG-DPP130002.
The authors acknowledge valuable discussion with Randy LeVeque, Marsha
Berger, and Hans-Petter Langtangen.  We also acknowledge David
Ketcheson and the KAUST sponsored HPC$^3$ numerics workshop at which
the initial phases of this project were first discussed.  The second
author would like to also acknowledge the Isaac Newton Institute
(Cambridge, UK), where much of the preliminary development work for
\forestclaw was done. The leaf/patch paradigm was independently
presented by B.\ as part of a talk at the SCI Institute, Salt Lake City, Utah,
USA in July 2011.

>>>>

\begin{figure}
\begin{center}
  \includegraphics[angle=-90,width=.8\columnwidth]{../figs_misc/omp.eps}
  \\[1ex]
  \includegraphics[angle=-90,width=.8\columnwidth]{../figs)misc/advance_strong_omp.eps}
\end{center}
\caption{Strong scaling of OpenMP parallelism for advection on a
  uniformly refined mesh.  Top: run time of advection Riemann problem kernel in both an optimized inlined interface and a generic function pointer interface via \manyclaw.  Bottom: MPI + OpenMp scaling results of advance kernel as above.
}
\label{fig:ompscale}
\end{figure}%

In \Fig{ompscale}, we scale intranode parallel calculations and in future iterations on accerelrators the \manyclaw set of solvers were compuled with \forestclaw.  \manyclaw provides a generic set of interators for Riemann problems and related algorithms. In this work we show good scaling results across a single node and coupled to the MPI scaling as well.

@@

We would like to thank the Texas Advanced Computing Center (TACC) for access to
the Stampede supercomputer under allocation TG-DPP130002 and TG-ASC130001 granted by the NSF XSEDE Program. 
The authors acknowledge valuable discussion with Randy LeVeque, Marsha
Berger, and Hans-Petter Langtangen.  We also acknowledge David
Ketcheson and the KAUST sponsored HPC$^3$ numerics workshop at which
the initial phases of this project were first discussed.  The second
author would like to also acknowledge the Isaac Newton Institute
(Cambridge, UK), where much of the preliminary development work for
\forestclaw was done. The leaf/patch paradigm was independently
presented by B.\ as part of a talk at the SCI Institute, Salt Lake City, Utah,
USA in July 2011. The fourth authors recognize Simula National Lab for funding.
